Generalized spaces for constructive algebra

### 2020-04-08 paper-herrsching2019/main.tex
Bohr topos

>>>>

The constructive Gelfand correspondence has been used to construct phase spaces
for quantum-mechanical systems in the Bohr topos approach to quantum
mechanics~\cite{butterfield-hamilton-isham:bohr,heunen-landsman-spitters:bohr,henry:bohr}.
Briefly, a quantum mechanical system is described by a~$C^\star$-algebra~$A$
which is in all interesting cases noncommutative. As such the Gelfand correspondence cannot be
applied to~$A$. But there is a mirror image of~$A$ as a sheaf model on a
certain locale, the \emph{Bohr topos} of~$A$, which \emph{is} commutative.
Since the universe of sheaves supports intuitionistic reasoning, as we will
review in Section~\ref{sect:sheaf-semantics}, the constructive Gelfand
correspondence can then be applied to this mirror image.
